Output Summary

### 2021-10-22 03-post-process/output-plots.Rmd
Insignificant changes to RMD

```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_nor)),
             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_nor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_nor]),
             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_hor)),
             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_hor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_hor]),
             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[.+,origin]$", origin = o_nor)),
             get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_nor], jags_data$BON_adults[observable,o_nor] - jags_data$LGR_adults[observable,o_nor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"))
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[.+,origin]$", origin = o_hor)),
             get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_hor], jags_data$BON_adults[observable,o_hor] - jags_data$LGR_adults[observable,o_hor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"))
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

>>>>

```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_nor)),
             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_nor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_nor]),
             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_hor)),
             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_hor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_hor]),
             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[.+,origin]$", origin = o_nor)),
             get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_nor], jags_data$BON_adults[observable,o_nor] - jags_data$LGR_adults[observable,o_nor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"))
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[.+,origin]$", origin = o_hor)),
             get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_hor], jags_data$BON_adults[observable,o_hor] - jags_data$LGR_adults[observable,o_hor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"))
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```
